---
title: "data_quality_assessment_malawi"
author: "ojgadabu"
date: "2/5/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r global_options, setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 8,
                      warning = FALSE, message = FALSE)
library(gplots)
library(cluster)
library(tidyverse)
library(pwr)
library(xtable)
library(stargazer)
library(knitr)
library(lubridate)
library(RMySQL)
library(stringr)
```
## Starting data quality assessment using the kahn framework with the data quality attributes of:

Completeness: Presence of data for an observation regardless of the structure or value of the data. For VL could be -100 or 700 or 200,000.
Conformance: Adherence of data to a predefined format or structure of the data. This could be domain of values, for example, VL not having a value of -20 which would be outside the domain of defined values.
Plausibility: This is the believability or truthfulness of observed data values, for example a patient with two viral load observations of 5000 and 700 within a space of a month. 



```{r echo=FALSE}
# read in a dataset with all its tables: 
# test code
#connect to local database to fetch validation tables for plausibility queries

 mydb = dbConnect(MySQL(), user='root', password='', dbname='validation_tables', host='localhost')
 
 setwd("~/Dropbox/dissertation_data_analysis/")



#QECH dataset
 id_data_table_qech           = read.csv("QECH_tables/qech_query_1.csv", stringsAsFactors = FALSE)
 drugs_data_table_qech        = read.csv("QECH_tables/qech_query_2.csv", stringsAsFactors = FALSE)
 bmi_data_table_qech   = read.csv("QECH_tables/qech_query_3.csv", stringsAsFactors = FALSE)
 adherence_data_table_qech     = read.csv("QECH_tables/qech_query_4.csv", stringsAsFactors = FALSE)

 
 #Kawale dataset
 #id_data_table_kawale           = read.csv("age_modified_kawale/kawale_query_1.csv", stringsAsFactors = FALSE)
 #drugs_data_table_kawale      = read.csv("age_modified_kawale/kawale_query_2.csv", stringsAsFactors = FALSE)
 #bmi_data_table_kawale = read.csv("age_modified_kawale/kawale_query_3.csv", stringsAsFactors = FALSE)
 #adherence_data_table_kawale   = read.csv("QECH_tables/qech_query_4.csv", stringsAsFactors = FALSE)
 
 #Completeness Proportions
 #Patient tracking variables
 
 id_data_table_qech$complete_address = ifelse(id_data_table_qech$district !="NULL" & id_data_table_qech$ta != "NULL" &     id_data_table_qech$village != "NULL", "Complete","Incomplete")
 

 
 total_number_of_patients = id_data_table_qech %>% nrow()
 number_of_complete_addresses = id_data_table_qech %>% filter(complete_address =="Complete") %>% nrow()
 address_completeness_proportion = number_of_complete_addresses/total_number_of_patients*100
 address_completeness_proportion
 
 id_data_table_qech$phone_number = ifelse(id_data_table_qech$cell_number !="NULL" & (id_data_table_qech$cell_number != "Unknown" |   id_data_table_qech$cell_number != "N/A"), "Complete","Incomplete")
 number_of_complete_phone_numbers = id_data_table_qech %>% filter(phone_number =="Complete") %>% nrow()
 phone_number_proportion = number_of_complete_phone_numbers/total_number_of_patients*100
 phone_number_proportion

 #completeness
 #Patient retention and health tracking
 #Denominator is all patient visits during the study period (January 2017 to December 2018). At minimum, each patient should have their vital signs measured when they visit the clinic. Therefore the denominator will be the number of encounters in the weight table.
 #BMI
 total_number_of_patient_visits = bmi_data_table_qech %>% nrow()
 number_of_complete_weight_observations = bmi_data_table_qech %>% filter(weight != "NULL") %>% nrow()
 proportion_complete_weight_documentation = number_of_complete_weight_observations/total_number_of_patient_visits * 100
 proportion_complete_weight_documentation
  
 
 #Prescription
 #Denominator will be total number of prescriptions made. A patient may have multiple prescriptions made on any single visit. In this case, the denominator differs with the weight denomina"tor where the expectation is a single value for each day.
 
 total_number_of_prescriptions = drugs_data_table_qech %>% nrow()
 #Analyze the denominator by month. Is it exhibiting similar average counts. Is there evidence to suggest that some records were not entered in some months for example over the study period. Plot of count of visits over two years.
 
 number_of_complete_prescriptions = drugs_data_table %>% filter(quantity != "NULL") %>% nrow() # NULL records indicate that the prescription was not filled. We take only complete prescriptions here.
 prescription_completeness_proportion = number_of_complete_prescriptions / total_number_of_prescriptions * 100
 prescription_completeness_proportion
 
 #Adherence
 
 #
 
 
 #Viral load
 #total number of patients that have been registered since the begining of the clinic to 6 months before the end of the study period
 #number of patients with a viral load reading documented in this period.
 
 viral_load_data_table_lh = read.csv("age_modified_kawale/LH_VL_results.csv", stringsAsFactors = FALSE)
 
 total_number_of_patients_lh = viral_load_data_table_lh %>% select(patient_id) %>% unique() %>% nrow()
 
 number_of_complete_viral_loads = viral_load_data_table_lh %>% filter(patient_VL_results != "") %>% select(patient_id) %>% unique %>% nrow()
 
 proportion_of_complete_vl_lh = number_of_complete_viral_loads/total_number_of_patients_lh * 100
 
 
 
 
 #Build the completeness data tables
 Variable_Names = c("Current Patient Address","Patient Mobile Phone Number","Weights of Patient","HIV Viral Load","Prescription Made","Drug Adherence")
 
 Numerators = c(number_of_complete_addresses,number_of_complete_phone_numbers,number_of_complete_weight_observations,number_of_complete_viral_loads,number_of_complete_prescriptions,"number_of_complete_adherence")
 
 Denominators = c(total_number_of_patients,total_number_of_patients,total_number_of_patient_visits,total_number_of_patients_lh,total_number_of_prescriptions,"total_number_of_patient_visits")
 
 Completeness_Proportions = c(address_completeness_proportion,phone_number_proportion,proportion_complete_weight_documentation,proportion_of_complete_vl_lh,prescription_completeness_proportion,"adherence")
 
 completeness_table = data.frame(Variable_Names,Numerators,Denominators,Proportions)
 
 
 
# cd$address_value = ifelse(cd$address_value == "Other"), "Other", cd$address_value))

 #What is the completeness of individual sections of patient address since it is divided into 3 parts. 
 
 cd = gather(id_data_table_qech,"address_section","address_value",2:4) 
 
 cd$address_value = ifelse((cd$address_value == "Other"), "Documented Other",cd$address_value)
 cd$address_value = ifelse((cd$address_value == "NULL"), "Not documented",cd$address_value)
 cd$address_value = ifelse((cd$address_value != "Documented Other" &  cd$address_value != "Not documented" ), "Address Unit Documented",      cd$address_value) 

 cd$address_section = as.factor(cd$address_section)
 cd$address_value = as.factor(cd$address_value)
 
 #Analyze the addresses as the field used for following up patients. Check the total number of patients that have been registered at each facility. Modification is that patient identifier no longer checked because HIV Testing Services (HTS) is not part of the available EMRs. Therefore check for total number of patients per site, then assess completeness of physical address as a set of "TA, district and village (current place of residence)"
#Patients with complete physical addresses. We define complete village as all addresses that have got the smallest unit of address which represents the current place of residence. Residents without current place of residence cannot be followed up if they miss an appointment. This is a threat to the second 90 of patient retention. 

 
ggplot(cd) + geom_bar(mapping = aes(x = address_section, fill = address_value), position = "dodge") + labs(title = "Completeness of Patient Address Components Documentation", x = "Patient Address Section", y = "Count of Documented Status", colour = "Documentation Status")  + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_blank(),panel.background = element_blank(), legend.title = element_blank())

# Are all visits captured in the EMR data or there are some dates where there are very low number of visits?
# count encounter dates and number of patient observed weight values for each date.

  bmi_data_table = mutate(bmi_data_table, new_encounter_date  =  as.Date(bmi_data_table$encounter_datetime, "%Y-%m-%d %T"))

  bmi_data_table$height = as.integer(bmi_data_table$height)
  bmi_data_table$weight = as.integer(bmi_data_table$weight)
  bmi_data_table$patient_id = as.integer(bmi_data_table$patient_id)
# Total number of patient encounter dates.
# Total number of weight observations
  
  
  by_month_all_encounters = bmi_data_table %>% group_by(yr = year(new_encounter_date),mn = month(new_encounter_date)) %>% dplyr::summarise(count = n())
  
  by_month_weights_documented = bmi_data_table %>%filter(weight > 0) %>%  group_by(yr = year(new_encounter_date),mn = month(new_encounter_date)) %>% dplyr::summarise(count_weights = n())
  
  by_month_heights_documented = bmi_data_table %>% filter(height > 0) %>%  group_by(yr =year(new_encounter_date),mn = month(new_encounter_date)) %>% dplyr::summarise(count_heights = n())
  
  
#plot number of encounters per day for each patient
#denominator for weight is all encounters. denominator for heights is the number of unique patients. Since an adult should have at least a single height.
#create a dataframe that has month name and number of encounters in that month
#then add to that dataframe number of weight and height observations per month
#After that then plot the graphs on one layer with different types of observations
#Should result in 3 line geoms. Expectation is that weight should be at each visit.

  combined_observations  = cbind(by_month_all_encounters,by_month_weights_documented) %>% cbind(.,by_month_heights_documented) %>% select(yr,mn,count,count_heights,count_weights)
  
  ggplot(combined_observations) + geom_line(aes(mn,count), size=1, color = "yellow") + geom_line(aes(mn,count_weights), size = 1, color = "blue")
  
  
  #ggplot(bmi_data_table, aes(x = new_encounter_date)) + geom_freqpoly(binwidth=1)

  
  
  
  
  #Plausibility. Are the data that have been built believable? Are they accurate
  
  #Patientaddress Plausibility.
  #Denominator will be the number of complete patient addresses.
  #Numerator, will be the number of addresses that fall within accepted addresses.
  mydb = dbConnect(MySQL(), user='root', password='', dbname='validation_tables', host='localhost')
  
  rs1 = dbSendQuery(mydb, "select * from village")
  all_villages <- fetch(rs1)
  dbClearResult(rs1)
  dbDisconnect(mydb)
  
  mydb = dbConnect(MySQL(), user='root', password='', dbname='validation_tables', host='localhost')
  rs2= dbSendQuery(mydb, "select * from traditional_authority")
  all_traditional_authorities = fetch(rs2)
  dbClearResult(rs2)
  dbDisconnect(mydb)
  
  mydb = dbConnect(MySQL(), user='root', password='', dbname='validation_tables', host='localhost')
  rs3 = dbSendQuery(mydb, "select * from district")
  all_districts = fetch(rs3)
  dbClearResult(rs3)
  dbDisconnect(mydb)
  
  complete_address
  
  #regular expression pattern for phone numbers. Filter those that are non numeric and are more than or less than 10 digits. 
  id_data_table_qech$plausible_phone_number = ifelse(str_length(id_data_table_qech$cell_number) == 10, "Plausible","Not Plausible")
  number_of_plausible_numbers = id_data_table_qech %>% filter(plausible_phone_number == "Plausible") %>% nrow()
  proportion_plausible_numbers = number_of_plausible_numbers/number_of_complete_phone_numbers*100
  
  
  #Atemporal Plausibility prescriptions
  #Number of prescriptions matching dispensed medicines
  #classify the prescriptions
  
  drugs_data_table_qech %>%
  select(patient_id:quantity) %>%
  mutate(
    type = case_when(
      name == "AZT/3TC/NVP (300/150/200mg tablet)" ~ "2A",
      name == "TDF/3TC/EFV (300/300/600mg tablet)" ~ "5A",
      name == "TDF/3TC (Tenofavir and Lamivudine 300/300mg tablet)" ~ "6A",
      name == "AZT/3TC/NVP (300/150/200mg tablet)" ~ "7A",
      name == "AZT/3TC/NVP (300/150/200mg tablet)" ~ "8A",
      name == "AZT/3TC/NVP (300/150/200mg tablet)" ~ "9A",
      TRUE                      ~  "other"
    )
  )
  
  
  #Plausible Viral load
  
  
  
  
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.









